Appendix B: Code for analysis comparing to historical data

### 2018-12-28 appendix/appendixB.Rmd
rebuild appendix B

```{r libraries, message=FALSE}
# devtools::install_github("boettiger-lab/sarsop")  ## install package first if necessary.
library(tidyverse)
library(sarsop)
library(nimble)
library(parallel)
library(gridExtra)
library(tictoc)
tic()
```

@@

```{r}
path <- unzip("ramlegacy.zip")
sheets <- readxl::excel_sheets(path)
ram <- lapply(sheets, readxl::read_excel, path = path)
names(ram) <- sheets
unlink("ramlegacy.zip")
unlink("RLSADB v3.0 (assessment data only).xlsx")
ramlegacy <- 
  ram$timeseries_values_views %>%
  select(assessid, stockid, stocklong, year, SSB, TC) %>%
  left_join(ram$stock) %>%
  left_join(ram$area) %>%
  select(assessid, stockid, scientificname, 
         commonname, areaname, country, year, 
         SSB, TC) %>%
  left_join(ram$timeseries_units_views %>%
              rename(TC_units = TC, SSB_units = SSB)) %>%
  select(scientificname, commonname, 
         stockid, areaname, country, year, 
         SSB, TC, SSB_units, TC_units)
```

@@

```{r}
options(mc.cores = parallel::detectCores()) # Reserve ~ 10 GB per core
log_dir <- "../data/appendixB"
```

@@

```{r}
models <- 
  parallel::mclapply(1:dim(meta)[1], 
                     function(i){
                       fisheries_matrices(
                         states = states,
                         actions = actions,
                         observed_states = observations,
                         reward_fn = reward_fn,
                         f = gs(meta[i, "r"][[1]], meta[i, "K"][[1]]),
                         sigma_g = meta[i,"sigma_g"][[1]],
                         sigma_m = meta[i,"sigma_m"][[1]],
                         noise = "normal")
                     })
```

@@

```{r message = FALSE, output = "hide"}
dir.create(log_dir, FALSE)
options(mc.cores = 1)

## POMDP solution (slow, >20,000 seconds per loop memory intensive)
system.time(
  alphas <- 
    parallel::mclapply(1:length(models), 
    function(i){
      log_data <- data.frame(model = "gs", 
                             r = meta[i, "r"][[1]], 
                             K = meta[i, "K"][[1]], 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal",
                             commonname = meta[i, "commonname"][[1]],
                             scenario = meta[i, "scenario"][[1]])

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 2e-8,
             timeout = 26000,
             log_dir = log_dir,
             log_data = log_data)
    })
)

@@

policy_pars <- 
  pars %>% 
  rowwise() %>% 
  do(statics(.))
```

@@

```{r}
system2("grep", c("MemTotal", "/proc/meminfo"), stdout = TRUE)
system2('grep', '"model name" /proc/cpuinfo', stdout = TRUE)
```

@@

```{r}
devtools::session_info()
```

>>>>

```{r libraries, message=FALSE}
# devtools::install_github("boettiger-lab/sarsop")  ## install package first if necessary.
library(tidyverse)
library(sarsop)
library(nimble)
library(parallel)
library(gridExtra)
library(tictoc)
library(furrr)
tic()
```

@@

```{r}
path <- unzip("ramlegacy.zip")
sheets <- readxl::excel_sheets(path)
ram <- lapply(sheets, readxl::read_excel, path = path)
names(ram) <- sheets

ramlegacy <- 
  ram$timeseries_values_views %>%
  select(assessid, stockid, stocklong, year, SSB, TC) %>%
  left_join(ram$stock) %>%
  left_join(ram$area) %>%
  select(assessid, stockid, scientificname, 
         commonname, areaname, country, year, 
         SSB, TC) %>%
  left_join(ram$timeseries_units_views %>%
              rename(TC_units = TC, SSB_units = SSB)) %>%
  select(scientificname, commonname, 
         stockid, areaname, country, year, 
         SSB, TC, SSB_units, TC_units)
```

@@

```{r}
options(mc.cores = 6) # Reserve ~ 10 GB per core
log_dir <- "../data/appendixB"
```

@@

```{r}
plan(multiprocess)

models <- 
  furrr::future_map(1:dim(meta)[1], 
                     function(i){
                       fisheries_matrices(
                         states = states,
                         actions = actions,
                         observed_states = observations,
                         reward_fn = reward_fn,
                         f = gs(meta[i, "r"][[1]], meta[i, "K"][[1]]),
                         sigma_g = meta[i,"sigma_g"][[1]],
                         sigma_m = meta[i,"sigma_m"][[1]],
                         noise = "normal")
                     })
```

@@

```{r message = FALSE, output = "hide"}
dir.create(log_dir, FALSE)
plan(multiprocess)
## POMDP solution 
system.time(
  alphas <- 
    furrr::future_map(1:length(models), 
    function(i){
      log_data <- data.frame(model = "gs", 
                             r = meta[i, "r"][[1]], 
                             K = meta[i, "K"][[1]], 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal",
                             commonname = meta[i, "commonname"][[1]],
                             scenario = meta[i, "scenario"][[1]])

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 2e-6,
             timeout = 25000,
             log_dir = log_dir,
             log_data = log_data)
    })
)

@@

policy_pars <- 
  pars %>% 
  transpose() %>% 
  map_df(statics)
```

@@

```{r include=FALSE}
## allow resizing output font in latex
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

```{r  size="tiny"}
system2("grep", c("MemTotal", "/proc/meminfo"), stdout = TRUE)
system2('grep', '"model name" /proc/cpuinfo', stdout = TRUE)
```

@@

```{r size="tiny"}
devtools::session_info()
```
